---
title: "EDA-AirBNB"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(ggplot2)
require(plotly)
```

#Checking Missing values
```{r Helper_Functions,echo=FALSE}
Missing = function(df){
  mresult=data.frame()
  for(each in colnames(df))
  {
    missingVal=sum(is.na(df[each]))
    data = data.frame(each,missingVal*100/nrow(df),nrow(unique(df[each])))
    mresult = rbind(mresult,data)
  }
  colnames(mresult)=c("Column Name","% Missing Values","# Unique Values")
  return(mresult)
}

PreProcess = function(train){
train$Booking=ifelse(train$country_destination=="NDF",0,1)
train$Native=as.factor(ifelse(train$language=="en","English","Non_english"))
train$US_NONUS=ifelse(train$country_destination=="NDF",NaN,ifelse(train$country_destination=="US","US","NON-US"))
train$US_NONUS=as.factor(train$US_NONUS)
train$Booking=as.factor(train$Booking)
#Fixing age
ifelse(train$age>100 | train$age<15,NaN,train$age)
train$AgeFac=as.factor(cut(train$age,seq(from = 0, to = 100, by = 20),include.lowest = TRUE))  
  return(train)
}

```

```{r summary,echo=FALSE}
train=read.csv("train.csv",na.strings=c("","NA"))
str(train)

Missing(train)
train=PreProcess(train)
train_dest=train[which(train$Booking==1),]
#Bin age into buckets

```
#Plot of gender
```{r gender , echo=FALSE}

 b=ggplot(data=train,aes(gender,fill=gender)) + ggtitle("Distribution of Gender")
 p1=b+geom_bar()
 ggplotly(p1)


b=ggplot(data=train,aes(gender,..count..)) + ggtitle("Gender vs Booking")
p2=b+geom_bar(aes(fill = train$Booking),position = "dodge")
ggplotly(p2)
```

#Plot of age
```{r age , echo=FALSE}
#Age has some noisy data like age >100 and age <15.We should replace such data with -1 or NA so that we can treat this data as missing data.
summary(train$age) 


y2=ggplot(train, aes(x = age)) +ggtitle("Distribution of Age")+
  geom_histogram(aes(y = ..count..), binwidth = 10,fill="blue") +
  scale_x_continuous(name = "Distribution of Age") +
  scale_y_continuous(name = "Count")+labs(fill = "Booking") 
ggplotly(y2)

b=ggplot(data=train,aes(AgeFac,..count..)) + ggtitle("Age vs Booking")
p2=b+geom_bar(aes(fill = train$Booking))+labs(fill = "Booking") 
ggplotly(p2)

b=ggplot(data=train_dest,aes(AgeFac,..count..)) + ggtitle("Age vs DESTINATION")
p2=b+geom_bar(aes(fill = train_dest$US_NONUS),position = "dodge")+labs(fill = "DESTINATION") 
ggplotly(p2)

```
#Plot of signup_method
```{r signup , echo=FALSE}

summary(train$signup_method) 

b=ggplot(data=train,aes(signup_method,..count..)) + ggtitle("Signup_Method vs Booking")
p2=b+geom_bar(aes(fill = train$Booking))+labs(fill = "Booking") 
ggplotly(p2)

b=ggplot(data=train_dest,aes(signup_method,..count..)) + ggtitle("Signup_Method vs US-NONUS")
p2=b+geom_bar(aes(fill = train_dest$US_NONUS),position="dodge")+labs(fill = "DESTINATION") 
ggplotly(p2)


#Plot of language
```{r signup_flow , echo=FALSE}
#Age has some noisy data like age >100 and age <15.We should replace such data with -1 or NA so that we can treat this data as missing data.
summary(train$language) 

b=ggplot(data=train,aes(language,..count..)) + ggtitle("language vs Booking")
p2=b+geom_bar(aes(fill=Booking),position = "dodge")+labs(fill = "Booking") 
ggplotly(p2)

b=ggplot(data=train_dest,aes(language,percent)) + ggtitle("Signup_Method vs US-NONUS")
p2=b+geom_bar(aes(fill = train_dest$US_NONUS),position="dodge")+labs(fill = "DESTINATION") 
ggplotly(p2)

